[dcpo_demsupport]

### 2020-08-08 paper/dcpo_demsupport.Rmd
estimate results

result_cls <- map(ls_mod, function(mod){
  result <- plm(ls_mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

@@

result_cls[3:4] <- map(ls_mod, function(mod){
  result <- pgmm(as.formula(ls_mod), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = sd.plm)
  df_result <- coef(result) %>% 
    tibble::enframe(name = "term", value = "estimate") %>% 
    mutate(std.error = vcovHC_se(result))
})

save(df_result_dcpo, file = here::here("output", "estimates_cls.RDS"))
```

>>>>

df_result_cls <- map(ls_mod, function(mod){
  result <- plm(ls_mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

@@

df_result_cls[3:4] <- map(ls_mod, function(mod){
  result <- pgmm(as.formula(ls_mod), effect="individual", model="onestep", transformation="ld", indexes=c("Country", "Year"), data = sd.plm)
  df_result <- coef(result) %>% 
    tibble::enframe(name = "term", value = "estimate") %>% 
    mutate(std.error = vcovHC_se(result))
})

save(df_result_cls, file = here::here("output", "estimates_cls.RDS"))
```
